Limb-darkening and exoplanets II: Choosing the Best Law for Optimal Retrieval of Transit Parameters

### 2016-01-19 which_law_2_use.tex
Corrected minor typos

\subsection{The bias-variance trade-off}
\begin{figure}
\includegraphics[scale=0.73]{which_law_to_use/bias_variance_plot.eps}
\caption{Sketch of each of the terms that define the bias and the precision of a given estimator. The probability density of the estimator $\hat{\theta}$ of 
the parameter $\theta$ is depicted in red, while the real, underlying value of the parameter $\theta$ is depicted with a black solid line. Ideally, one would 
want a low bias, high precision estimator.{\bf TBD Here under sqrt(variance) it should say 1/precision}}
\label{bias-variance-plot}
\end{figure}

@@

Given that the study of the mean-squared error is complex from a mathematical point of view for our case, we study it through simulations similar to the ones done in the past sub-section, 
but this time also adding different amounts of noise to the lightcurves in order to derive the variances of the estimators for a given level of noise. We take a Monte Carlo approach in order to study 
the MSE. As a case study, we take that of a typical Hot-Jupiter ($p=0.1$, $a_R = 10$) around a Solar-type star ($T_\textnormal{eff}= 5500$ K) on a low impact-parameter orbit ($b=0.3$), 
and we focus specifically on the retrieval of the planet-to-star radius ratio, which is one of the most interesting parameters retrieved from transit lightcurves. We simulate a suite of 
lightcurves with noise levels ranging from $10$ ppm to $3000$ ppm with different amount of in-transit points. We show our results for $N=100$ and $N=1000$ in-transit 
points, which span a range of possible scenarios for both space based (e.g., \textit{Kepler}) and ground-based observations. For each case, $300$ lightcurves are generated, 
and all of them are fitted in the same way as it was done for their noiseless counterparts in the past sub-section. From the fit to each of the $300$ lightcurves on each case, 
we take all the estimated planet-to-star radius ratios and estimate the variance of the sample. The results of our simulations are shown on Figure~\ref{biasvariance}, where we plot the 
MSE as a function of the noise of the simulated lightcurves for each of the limb-darkening law used to retrieve the parameter.

@@

From our case study, we propose that the selection of the optimal limb-darkening law in a MSE sense can be estimated by simple simulation:  for a given observational setup in terms of cadence and noise, simply calculate the MSE obtained 
by all the laws and select the one that gives the minimum MSE. However, we note that different transit geometries will give rise to different optimal limb-darkening laws at a given 
lightcurve precision and, thus, these simulations must be performed on a case-by-case basis. Of course, for this case-by-case study a set of transit parameters are needed as 
inputs, which is a bit circular as this is what we are trying to extract from a transit lightcurve. However, as we learned from our results on this and the past sub-sections, it is important 
to remember that the functional relation of the transit parameters and the biases/variances is smooth and slow. Therefore, one can first fit with one favourites' law, obtain a set of transit parameters, and use those as inputs in order to calculate the MSE of 
different limb-darkening laws in order to then retrieve the final transit parameters from the law that gives the lowest MSE. We provide code at Github with which this process be easily done 
for a given set of transit and stellar parameters, along with a given lightcurve noise level and number of in-transit points.

>>>>

\subsection{The bias-variance trade-off}
\begin{figure}
\includegraphics[scale=0.73]{which_law_to_use/bias_variance_plot.eps}
\caption{Sketch of each of the terms that define the bias and the precision of a given estimator. The probability density of the estimator $\hat{\theta}$ of 
the parameter $\theta$ is depicted in red, while the real, underlying value of the parameter $\theta$ is depicted with a black solid line. Ideally, one would 
want a low bias, high precision estimator.}
\label{bias-variance-plot}
\end{figure}

@@

Given that the study of the mean-squared error is complex from a mathematical point of view for our case, we study it through simulations similar to the ones done in the past sub-section, 
but this time also adding different amounts of noise to the lightcurves in order to derive the variances of the estimators for a given level of noise. We take a Monte Carlo approach in order to study 
the MSE. As a case study, we take that of a typical Hot-Jupiter ($p=0.1$, $a_R = 10$) around a Solar-type star ($T_\textnormal{eff}= 5500$ K) on a low impact-parameter orbit ($b=0.3$), 
and we focus specifically on the retrieval of the planet-to-star radius ratio, which is one of the most interesting parameters retrieved from transit lightcurves. We simulate a suite of 
lightcurves with noise levels ranging from $10$ ppm to $3000$ ppm with different amount of in-transit points. We show our results for $N=100$ and $N=1000$ in-transit 
points, which span a range of possible scenarios for both space based (e.g., \textit{Kepler}) and ground-based observations. For each case, $300$ lightcurves are generated, 
and all of them are fitted in the same way as it was done for their noiseless counterparts in the past sub-section. From the fit to each of the $300$ lightcurves on each case, 
we take all the estimated planet-to-star radius ratios and estimate the variance of the sample. The results of our simulations are shown on Figure~\ref{biasvariance}, where we plot the 
MSE as a function of the noise of the simulated lightcurves for each of the limb-darkening laws used to retrieve the parameter.

@@

From our case study, we propose that the selection of the optimal limb-darkening law in a MSE sense can be estimated by simple simulation:  for a given observational setup in terms of cadence and noise, simply calculate the MSE obtained 
by all the laws and select the one that gives the minimum MSE. However, we note that different transit geometries will give rise to different optimal limb-darkening laws at a given 
lightcurve precision and, thus, these simulations must be performed on a case-by-case basis. Of course, for this case-by-case study a set of transit parameters are needed as 
inputs, which is a bit circular as this is what we are trying to extract from a transit lightcurve. However, as we learned from our results on this and the past sub-sections, it is important 
to remember that the functional relation of the transit parameters and the biases/variances is smooth and slow. Therefore, one can first fit with one favourites' law, obtain a set of 
transit parameters, and use those as inputs in order to calculate the MSE of different limb-darkening laws in order to then retrieve the final transit parameters from the law that gives 
the lowest MSE. We provide code at Github with which this process can be easily done for a given set of transit and stellar parameters, along with a given lightcurve noise level and 
number of in-transit points.
